%------------------------------------------------------------------------------
% Define title, author(s), affiliation and publishing status
%
\papertitle[Scaling of TBLs spectra] % Short title used in headlines (optional)
{%
  New insight into the spectra of turbulent boundary layers with pressure gradients% THE COMMENT SYMBOL AT THE END OF THIS LINE IS NEEDED
}%
%
\papertoctitle{New insight into the spectra of turbulent boundary layers \\ with pressure gradients} % Title for toc
%
\paperauthor[R. Pozuelo, Q. Li, P. Schlatter \& R.Vinuesa] % Short authors used in headlines and List Of Papers
{%
  Ram\'on Pozuelo$^1$, Qiang Li$^1$, Philipp Schlatter$^1$ and Ricardo Vinuesa$^1$%
}%
%
%\listpaperauthor{A. Skywalker \& D. Vader}% (optional) Short authors used in List Of Papers
%
\paperaffiliation
{%
  $^1$ FLOW, Engineering Mechanics, KTH Royal Institute of Technology, SE-100 44 Stockholm, Sweden
}%
%
\paperjournal[Phys. Rev. Letters] % Short publish info used in List Of Papers
{%
	Physical Review Letters%
}%
%
\papervolume{A4}%
%
\papernumber{B4}%
%
\paperpages{C4}%
%
\paperyear{2022}%
%
\papersummary%
{% Insert summary of the paper here (used in introduction) 
	D4
}%
% 
\graphicspath{{paper4/figs}}%
%
%
%===============================================================================
%                            BEGIN PAPER
%===============================================================================
%
\begin{paper}

\makepapertitle

%------------------------------------------------------------------------------
% Abstract
%------------------------------------------------------------------------------
%
\begin{paperabstract}
	With the availability of new high-Reynolds-number ($Re$) databases of turbulent boundary layers (TBLs) it has been possible to identify in detail certain regions of the boundary layer with 
more complex behavior. In this study we consider a unique database at moderately-high $Re$, with a near-constant adverse pressure gradient (APG) (Pozuelo {\it et al.}, {\it J. Fluid Mech.}, {\bf 939}, A34, 2022), and perform spectral analysis of the Reynolds stresses, focusing on the streamwise component. We assess different regions of the APG TBL, comparing this case with the zero-pressure-gradient (ZPG) TBL, and identify the relevant scaling parameters as well as the contribution of the scales of different sizes. 
The small scales in the near-wall region up to the near-wall spectral peak have been found to scale using viscous units.
In APG TBLs, the largest scales close to the wall have a better scaling with the boundary-layer thickness ($\delta_{99}$), and they are significantly affected by the APG.
In the overlap and wake regions of the boundary layer, the small energetic scales exhibit a good scaling with the displacement thickness ($\delta^*$) while the larger scales and the outer spectral peak are better scaled with the boundary-layer thickness. Also, note that the wall-normal location of the spectral outer peak scales with the displacement thickness rather than the boundary layer thickness. The various scalings exhibited by the spectra in APG TBLs are reported here for the first time, and shed light on the complex phenomena present in these flows of great scientific and technological importance.
\end{paperabstract}


%------------------------------------------------------------------------------
% Article
%------------------------------------------------------------------------------
%
\input{paper4/article.tex}


%------------------------------------------------------------------------------
% Bibliography
%------------------------------------------------------------------------------
%
%\clearpage
\bibliographystyle{jfm}
\bibliography{thesis}
%
% \IfFileExists{paper2/paper.bbl}{\input{paper2/paper.bbl}}{}

%===============================================================================
%                            END PAPER
%===============================================================================
\end{paper}
