%-------------------------------------------------------------------------------
% Cover page
%-------------------------------------------------------------------------------
%
\makecoverpage


%-------------------------------------------------------------------------------
% Dedication (comment if none)
%-------------------------------------------------------------------------------
%
\dedication{
	{\it ``All izz well.''}\\[20pt]
	From the movie ``3 idiots''
}


%-------------------------------------------------------------------------------
% Abstract (English)
%-------------------------------------------------------------------------------
%
% COMMENT: the abstract should be limited to 2000 characters and the keywords
% to 250 characters because otherwise they will not fit in the mailing sheet.
%
\begin{abstract}
\highlight{
    Turbulent boundary layers are present in many aspects of life, from the weather and wind currents to transportation, production of energy or mixing processes. Understanding turbulent motions can allow for an improvement and development of technical devices, techniques or diagnosis of phenomena where a fluid is in a turbulent regime. 
    From an economic and environmental perspective, knowledge on turbulent boundary layers may help to reduce the drag in aerodynamic surfaces in transportation that lead to a reduction of fuel consumption and pollution.
    It is also possible to enhance the production of energy from wind sources or the harvest of tidal energy.
    Other turbulent motions that has been recently impacted society are those related with diffusion such as the transport of aerial diseases, or the motions of air in the respiratory system.
    In all those examples, external pressure gradients or those produced by the curvature of wall surfaces affects the turbulent structures and thus, the outputs that we study such as drag, transport of substances, output of energy...
    A relevant case is that of adverse pressure gradients which enhance the wall-normal convection and redistribute the turbulent energy across the turbulent boundary later. 
    We study here a canonical case for adverse-pressure gradient turbulent boundary layers, which is the flow over a flat plate, under near-equilibrium adverse-pressure gradient conditions.
    We have extended the previous datasets on flat plate boundary layers under adverse pressure gradients which were obtained at low Reynolds numbers, with a new numerical simulation reaching high Reynolds numbers compared to experimental results.
    This new dataset allowed to study both adverse-pressure gradient and Reynolds number effects, where the thicker boundary layer shows a clear separation of turbulent of scales.
    The influence of the size of the domain and the wider turbulent scales are analyzed through a set of turbulent channel flow simulations and the spectral analysis of the Reynolds stresses in large Reynolds numbers turbulent boundary layers.
    The impact of the wider scales was analyzed and scaling factors where found for different regions of the spectra of the Reynolds stresses, specially the energy of the small scales that have been advected to the outer region of the boundary layer.
    We also present a discussion on the cascading process of the turbulent energy between scales, and give some results for adverse-pressure gradients.
    }
		%
		\keywords{numerical simulations, turbulence, adverse-pressure gradients, boundary layers.}
		%
\end{abstract}


%-------------------------------------------------------------------------------
% Abstrakt (Swedish) 
%-------------------------------------------------------------------------------
%
% COMMENT: the abstract should be limited to 2000 characters and the keywords
% to 250 characters because otherwise they will not fit in the mailing sheet.
%
\begin{abstrakt}
\rev{
	\r{A}tkomstpunkter m\r{a}ste arbeta. I sj\"{a}lva verket skulle f\r{a}
	kryptografer h\r{a}ller inte med emulering av robotar, som
	f\"{o}rkroppsligar de tekniska principer av komplexitetsteori. Hyp, v\r{a}r
	nya applikation f\"{o}r f\"{o}rlustfri information är l\"{o}sningen på alla
	dessa utmaningar.
		%
		\nyckelord{super-lasrar, rymdstationer, Kraften, kakor.}
		%
		}
\end{abstrakt}


%-------------------------------------------------------------------------------
% Preface page
%-------------------------------------------------------------------------------
%
\begin{preface}
\highlight{
    This thesis gives an initial introduction to turbulent boundary layers, and the statistical approach used to study to turbulence.
    The different turbulent statistics are shown and analyzed for adverse-pressure gradient turbulent boundary layers, and the effects of adverse pressure gradient and Reynolds numbers are discussed thanks to the large Reynolds number databases.
    The spectral decomposition of the Reynolds stresses is introduced to further understand the hidden mechanism and scaling that leads to differences in the Reynolds stresses of zero and adverse-pressure gradient turbulent boundary layers.
    Another effect of pressure gradients is the impact on the skin-friction coefficient. We present two approaches, that analyze different sources for the skin-friction coefficient and how the adverse-pressure gradient modifies these terms.
    The impact of the wider scales have been proven essential at large Reynolds numbers and also with adverse-pressure gradients, we also analyze the effect of the width of the domain to capture these wide scales through a set of turbulent channel flows.
    
    The respective publications in part II are adjusted to the same format to maintain consistency along the thesis, but the content remains unaltered compared to the original counterparts.
}

\end{preface}


%-------------------------------------------------------------------------------
% Division of work between authors
%-------------------------------------------------------------------------------
%
\begin{divisionofwork}
\highlight{
	The main advisor for the project is Ricardo Vinuesa Motilva (RV) with Philipp Schlatter (PS) as co-advisor.
	\paperitem
		The set-up of the simulation was done by Ram\'on Pozuelo (RP) and Qiang Li (QL). The boundary conditions and MPI single precision communication were implemented by PS and RP. The simulation, post-processing codes and analysis where performed by RP. The papers was written by RP with comments and inputs from RV, PS and QL. \rev{reviewer from JFM?}

	\paperitem
		The post-processing scripts for the spectral analysis where written by RP based on previous scripts by PS. The MCE analysis was proposed by RP. The paper was written by RP with inputs from RV, PS and QL.
		
	\paperitem
	    The data-set has been analysed by Yitong Fan (YF), with input from Weipeng Li (WL), and from Marco Atzori (MA) (for the NACA4412 data-set) and Ramon Pozuelo (RP, for the APG data-set). The paper has been written by YF, with input from WL. WL and RV initiated the work. WL, MA, RP, PS, and RV revised the manuscript and provided feedback.
	    
	\paperitem
	    The mathematical framework has been proposed by MA, with databases from Ferm\'in Mallor (FM) and RP. The paper has been written by MA, with additional input from Alexander Stroh (AS), Davide Gatti (DG), Koji Fukagata (KF), RV and PS.

}
\end{divisionofwork}


%-------------------------------------------------------------------------------
% Additional publications (comment if none)
%-------------------------------------------------------------------------------
%
% \begin{otherpublications}
% 	The following papers, although related, are not included in this thesis.

%   \paperitem%
%     {Anakin Skywalker \& Master Obi-Wan Kenobi}% Authors
%     {3639}% Year
%     {The light sabre: an elegant weapon for a more civilized age}% Title
%     {Jedi Journal of Weapons}% Journal
%     {33}% Volume
%     {2}% Number
%     {pp. 55--60}% Pages

% \end{otherpublications}


%-------------------------------------------------------------------------------
% Conferences (comment if none)
%-------------------------------------------------------------------------------
%
\begin{conferences}
	Part of the work in this thesis has been presented at the following 
	international conferences. The presenting author is underlined.

  \conferenceitem%
    {\underline{Ram\'on Pozuelo}, Qiang Li, Sergio Hoyas, Philipp Schlatter \& Ricardo Vinuesa}% Authors
    {2019}% Year
    {Towards efficient wall-bounded turbulence simulations}% Title
    {Svenska mekanikdagar}% Conference
    {Stockholm}% Location
    
  \conferenceitem%
    {\underline{Ram\'on Pozuelo}, Qiang Li, Philipp Schlatter \& Ricardo Vinuesa}% Authors
    {2020}% Year
    {An adverse-pressure-gradient turbulent boundary layer with nearly-constant $\beta \simeq 1.4$ up to $Re_{\theta} \simeq 8,700$}% Title
    {73rd Annual Meeting of the APS Division of Fluid Dynamics}% Conference
    {Online}% Location
    
  \conferenceitem%
    {\underline{Ram\'on Pozuelo}, Qiang Li, Philipp Schlatter \& Ricardo Vinuesa}% Authors
    {2021}% Year
    {Spectral analysis of a high-Reynolds-number near-equilibrium adverse-pressure-gradient turbulent boundary layer}% Title
    {74th Annual Meeting of the APS Division of Fluid Dynamics}% Conference
    {Phoenix, Arizona, U.S.}% Location
    
  \conferenceitem%
    {\underline{Ram\'on Pozuelo}, Qiang Li, Philipp Schlatter \& Ricardo Vinuesa}% Authors
    {2022}% Year
    {On the influence of spanwise spectral scales in the Reynolds stress statistics in adverse-pressure gradient turbulent boundary layers.}% Title
    {1st Spanish Fluid Mechanics Conference}% Conference
    {C\'adiz}% Location
\end{conferences}

%-------------------------------------------------------------------------------
% Table of contents
%-------------------------------------------------------------------------------
%
\tableofcontents
